So you want to build a search engine?

### 2018-05-27 Algebra/Homework/Homework.tex
backup

\subsubsection{Question 14}
%TODO Fermat's little theorem, I have combinatorial proof but inductive evades me

@@

By lemma 1.7.3 from the book we know that $\abs{uv} = \abs u\abs v$, therefore, as $zz^{-1} = 1$ we also have $\abs{zz^{-1}} = 1$ so $\abs z\abs{z^{-1}} = 1$ and it follows $\abs {z^{-1}} = 1 / \abs z$.

%Get help from Russos?
By Euler's equation we know that $\cos\theta + i\sin\theta = e^{i\theta}$. We have ${\left(e^{i\theta}\right)}^m = e^{im\theta} = \cos (m\theta) + i\sin (m\theta)$

>>>>

Let $n = 0$, then it is trivial that $n^p - n$ is divisible by $p$ for any prime $p$.

Now let $n$ be a fixed non-negative integer, and assume that $n^p-n$ is divisible by $p$ for any prime $p$. By the binomial theorem we have
\begin{align*}
(n+1)^p - (n+1)
&= \sumfrom{i=0}{p}{\binom{p}{i}n^i}-n-1 \\
&= \sumfrom{i=1}{p-1}{\binom{p}{i}n^i}+n^p+1-n-1 \\
&= \sumfrom{i=1}{p-1}{\binom{p}{i}n^i}+\left(n^p-n\right)
\end{align*}
By our assumption we have $n^p-n$ is divisible by $p$. Additionally $\binom pi$ must be divisible by $p$ for all $0 < i < p$ because $\binom pi = \frac{p!}{i!(p-i)!}$ and $p$ is prime.

By induction we then know that $n^p-n$ is divisible by $p$ for any prime $p$.

@@

\subsubsection{Question 3}
Using Lemma 1.7.1, the fact that $\overline 1 = 1$, and some group axioms, we get.
\begin{align*}
1 &= (\overline z)^{-1}\overline z \\
\therefore \overline 1 &= \overline{(\overline z)^{-1}\overline z} \\
&= \overline{(\overline z)^{-1}}\cdot\overline{(\overline z)} \\
&= \overline{(\overline z)^{-1}} \cdot z \\
\therefore z^{-1} &= \overline{(\overline z)^{-1}} \\
\therefore \overline{z^{-1}} &= \overline{\left(\overline{(\overline z)^{-1}}\right)} \\
&= (\overline z)^{-1}
\end{align*}

\subsubsection{Question 6}

For any $z \in\mathbb C$, there exists $a,b\in\mathbb R$ such that $z = a+bi$. Now $\overline z = a-bi$ by definition. Therefore $z = \overline z$ iff $b=0$ as $a-bi = a+bi$ iff $b=0$. Finally if $b=0$ then $z = a$ and therefore $z$ is real, if $b\not=0$ then $z=a+bi$ for some non-zero $b\in\mathbb R$ so $z$ has an imaginary part and is not real. Therefore we have shown that $z = \overline z$ iff $z\in\mathbb R$.

Now if $a=0$ the we say that $z$ is purely imaginary as there is no real part to $z$. So if $z$ is purely imaginary then $z = bi$ and $\overline z = -bi = -z$. If we start with $\overline z = -z$ then we get 
\begin{align*}
-(a+bi) &= a-bi \\
-a-bi &= a-bi \\
-a = a\\
a = 0
\end{align*}
so $z$ must be purely imaginary. Putting this all together we get that $-z=\overline z$ iff $z$ is purely imaginary.

%\subsubsection{Question 8}

%By lemma 1.7.3 from the book we know that $\abs{uv} = \abs u\abs v$, therefore, as $zz^{-1} = 1$ we also have $\abs{zz^{-1}} = 1$ so $\abs z\abs{z^{-1}} = 1$ and it follows $\abs {z^{-1}} = 1 / \abs z$.

\subsubsection{Question 11}

\question{(a)} $z = \cos\frac{7\pi}4 + i\sin\frac{7\pi}{4}$

\question{(b)} $z = 4\left(\cos \frac\pi2 + i\sin \frac\pi2\right)$

\question{(c)} $z = 36\left(\cos \frac\pi4 + i\sin \frac\pi4\right)$

\question{(d)} $z = 13\left(\cos \frac{2\pi}3 + i \sin\frac{2\pi}3 \right)$

\subsubsection{Question 13}
\begin{align*}
\left(\frac12 + \frac12\sqrt3i\right)^3 &= \left(\frac12\left(1+\sqrt3i\right)\right)^3 \\
&= \frac18\left(1+\sqrt3i\right)^3 \\
&= \frac18\left( 1 + 3\sqrt3i+ 3\left(\sqrt3i\right)^2 + \left(\sqrt3i\right)^3 \right) \\
&= \frac18\left( 1 + 3\sqrt3i - 9 - 3\sqrt3i \right) \\
&= \frac18\left(-8\right) \\
&= -1
\end{align*}

%\subsubsection{Question 14}

%Get help from Russos?
%By Euler's equation we know that $\cos\theta + i\sin\theta = e^{i\theta}$. We have ${\left(e^{i\theta}\right)}^m = e^{im\theta} = \cos (m\theta) + i\sin (m\theta)$

\subsubsection{Question 20}

Let us adopt the notation that for any $c\in\mathbb C$, $$c = c_a + c_bi$$ where $c_a,c_b\in\mathbb R$.
\begin{align*}
\abs{z+w}^2+\abs{z-w}^2 &= \abs{z_a+z_bi + w_a+w_bi}^2 + \abs{z_a+z_bi - w_a-w_bi}^2 \\
&= (z_a+w_a)^2+(z_b+w_b)^2+(z_a-w_a)^2+(z_b-w_b)^2 \\
&= {z_a}^2+2z_aw_a+{w_a}^2 + {z_b}^2+2z_bw_b+{w_b}^2 +{z_a}^2-2z_aw_a+{w_a}^2 + {z_b}^2-2z_bw_b+{w_b}^2 \\
&= 2\left({z_a}^2+{a_b}^2+{w_a}^2+{w_b}^2\right)\\
&= 2\left( \abs{z}^2 + \abs{w}^2 \right)
\end{align*}

Our approach here is to partition $A$ into countably many finite sets, this will show that there is a 1-1 and onto correspondence from $A$ to $\mathbb N$ as they are both countably infinite. We define $\abs{a+bi}_1 = \abs a + \abs b$. Now we define the set $Z_k = \setbuilder{z\in A}{\abs{z} = k}$ for $k \in\mathbb N \union\set0$. Now for all $z\in A$, there exists some $k\in\mathbb N \union\set 0$ such that $z\in Z_k$ as for any $z\in A$, $z = a+bi$ for $a,b\in\mathbb Z$ and therefore $\abs{z} = \abs{a} + \abs{b} \in \mathbb N \union \set 0$ so there is some $k\in\mathbb N \union\set 0$ such that $z \in Z_k$. For any $k\in\mathbb N\union\set 0$ we also have $Z_k$ is finite as for all $a+bi \in Z_k$, $\abs a\le k$ and $\abs b \le k$, therefore there are only finitely many possibilities for $a$ and $b$. Now we have $\unionacross{k\in\mathbb N \union\set 0}{Z_k} = A$ with each $Z_k$ finite, so $A$ must be countable.

\subsubsection{Question 22}

First we will prove that $P(\overline x) = \overline{P(x)}$ for any polynomial $P:\mathbb C \to \mathbb C$ with real coefficients, $\alpha_0, \alpha_1,\ldots,\alpha_n$. Let $z \in \mathbb C$ such that $z = a+bi$ with $a$ and $b$ real. Notice that for any $\alpha\in\mathbb R$, 
\begin{align*}
\alpha\overline z &= \alpha(a - bi) \\
&= \alpha a - \alpha bi \\
&= \overline{\alpha z}
\end{align*}
From lemma 1.7.1 we get $\overline{zw} = \overline z \overline w$, so it follows that $\overline{z^n} = \overline{z}^n$. Finally from lemma 1.7.1 we also get $\overline {z + w} = \overline z + \overline w$ so it follows that $\overline{\sum z_j} = \sum \overline{z_j}$. So if $P(x) = \sumfrom{j=0}{n}{\alpha_jx^j}$ then it follows
\begin{align*}
P(\overline{x}) &= \sumfrom{j=0}{n}{\alpha_j\overline x^j} \\
&= \sumfrom{j=0}{n}{\alpha_j\overline{x^j}} \\
&= \sumfrom{j=0}{n}{\overline{\alpha_jx^j}} \\
&= \overline{\sumfrom{j=0}{n}{\alpha_jx^j}} \\
&= \overline{P(x)}
\end{align*}

Therefore if we have any polynomial $P$ with real coefficients, and $P(x) = 0$ then $P(\overline x) = \overline 0 = 0$.

\section{Chapter 2}
\subsection{Section 1}
\subsubsection{Question 8}
Let us start with when $n=0$, then $(a*b)^n = e = a^n*b^n$.

For $n > 0$ we will do induction, so let us assume that $(a*b)^{n-1} = a^{n-1}*b^{n-1}$, therefore 
\begin{align*}
(a*b)^n &= (a*b)^{n-1}*(a*b) \\
&= (a^{n-1}*b^{n-1}) * (a * b) \\
&= (a^{n-1} * a) * (b^{n-1} * b) \\
&= a^n * b^n
\end{align*}
as we already have the case $n=0$ this induction proves the statement for $n\ge 0$.

Now assume $n<0$, therefore $a^n = \left(a^{-1}\right)^{-n}$ and as $a^{-1} \in G$ and $-n > 0$ then we simply refer to our previous work and conclude that the statement still holds.

Let $a,b\in G$.
\begin{align*}
e &= (a*b)^2 \\
e &=  a^2 \\
e &= b^2 \\
e &= e * e \\
&= a^2 * b^2\\
a^2 * b^2 &= (a*b)^2\\
a*a*b*b &= a*b*a*b \\
a^{-1}*a*a*b*b*b^{-1} &= a^{-1}*a*b*a*b*b^{-1}\\
a*b &= b*a
\end{align*}

We simply list off all elements of $S_3$ as $S_3$ is small.

\begin{tabular}{c|c|c}
	$x\in S_3$ & Does $x^2 = e$ & Does $x^3 = e$ \\
	\hline
	$(1,2,3)$ & Yes & Yes \\
	$(1,3,2)$ & Yes & No \\
	$(2,1,3)$ & Yes & No \\
	$(2,3,1)$ & No & Yes \\
	$(3,2,1)$ & Yes & No \\
	$(3,1,2)$ & No & Yes \\
\end{tabular}

\subsubsection{Question 20}
This is all elements $p\in S_4$ such that there does not exist exactly one $x$ such that $p(x) = x$.
\begin{enumerate}
	\item $(1,2,3,4)$
	\item $(1,2,4,3)$
	\item $(2,1,3,4)$
	\item $(2,1,4,3)$
	\item $(1,4,3,2)$
	\item $(3,2,1,4)$
	\item $(3,4,1,2)$
	\item $(1,3,2,4)$
	\item $(4,2,3,1)$
	\item $(4,3,2,1)$
	\item $(2,3,4,1)$
	\item $(2,4,1,3)$
	\item $(3,4,2,1)$
	\item $(3,1,4,2)$
	\item $(4,1,2,3)$
	\item $(4,3,1,2)$
\end{enumerate}
\subsubsection{Question 26}

Let $G$ be a finite group. Assume for the sake of contradiction that there is some $a\in G$ such that for all $n \in\mathbb N$, $a^n\not= e$. As $G$ is finite there then must be some $n_1\not=n_2$ such that $a^{n_1} = a^{n_2}$ by the pigeon hole principle. Let us assume without loss of generality that $n_2 > n_1$, it follows then that $a^{n_1}*a^{-n_1} = a^{n_2}*a^{-n_1}$ and therefore $e = a^{n_2 - n_1}$. This means we have a contradiction and therefore there exists some $n\in\mathbb N$ such that $a^n=e$ for any $a \in G$.

\subsubsection{Question 27}

We already have shown that each element $a\in G$ has some specific $n_a$ such that $a^n = e$. It follows then that if $m = {\prodacross{a\in G}{n_a}}$ then $a^m = e$ for all $a\in G$.
\begin{proof}
	Choose $a \in G$ and let $m = \prodacross{g\in G}{n_g}$. Now $a^m = a^{(m/n_a)(n_a)}$, and for notation let $m_a = \frac m{n_a}$. We now have
	\begin{align*}
	a^m &= a^{n_a\cdot m_a} \\
	&= \left(a^{n_a}\right)^{m_a} \\
	&= e^{m_a} \\
	&= e
	\end{align*}
\end{proof}

First we know that for any $a \in G$ there exists some $a^{-1} \in G$ such that $a^{-1} a = e$ We will adopt this notation as well as simply saying $ab = a * b$ for $a,b\in G$. Now we have
\begin{align*}
aa^{-1}aa^{-1} &= aea^{-1} \\
&= aa^{-1} \\
\therefore \left(aa^{-1}\right)^{-1}aa^{-1} &= \left(aa^{-1}\right)^{-1}aa^{-1}aa^{-1} \\
\therefore e &= aa^{-1}
\end{align*}

Next we wish to prove some a lemma. If $ab = ac$ then $b = c$
\begin{proof}
	\begin{align*}
	ab = ac &\implies a^{-1}ab = a^{-1}ac \\
	&\implies eb=ec \\
	&\implies b = c
	\end{align*}
\end{proof}

Now with this we can say that for all $a \in G$, there exists exactly one inverse as if $ab = e = ac$, then $b = c$. We also can say an element $a\in G$ is the inverse of exactly one element by the exact same proof.

Finally we get
\begin{align*}
aea^{-1} &= aa^{-1} \\
&= e \\
\therefore a^{-1} &= (ea)^{-1} \\
\therefore a &= ea
\end{align*}

\subsection{Section 2}
\subsubsection{Question 1}
\subsubsection{Question 2}
\subsubsection{Question 5}

\subsection{Section 3}
\subsubsection{Question 4}
\subsubsection{Question 5}
\subsubsection{Question 11}
\subsubsection{Question 22}
\subsubsection{Question 24}
\subsubsection{Question 26}
\subsubsection{Question 28}
\subsubsection{Question 29}

\subsection{Section 4}
\subsubsection{Question 1}
\subsubsection{Question 5}
\subsubsection{Question 18}
\subsubsection{Question 24}
\subsubsection{Question 30}
\subsubsection{Question 35}
\subsubsection{Question 37}
\subsubsection{Question 38}
\subsubsection{Question 42}
\subsubsection{Question 43}

\subsection{Section 5}
\subsubsection{Question 3}
\subsubsection{Question 17}
\subsubsection{Question 18}
\subsubsection{Question 19}
\subsubsection{Question 24}
\subsubsection{Question 26}
\subsubsection{Question 29}
\subsubsection{Question 38}
\subsubsection{Question 42}

### 2018-05-27 NetworkScience/Final/Final.tex
backup

	\begin{abstract}
		There are many different types of search engines, the most complicated of which are where you do not initially have knowledge of what is being searched and that information may change. In order to tackle this we need some way of discovering possible results, matching these results to a query and ranking possible results. This paper deals largely with the discovery and more specifically a process called web crawling.
	\end{abstract}

>>>>

	\begin{abstract}
		There are many different types of search engines for many different use cases. In this paper will investigate how one may make a search engine for the Internet or a similar entity. In doing this we need some way of discovering possible results, matching these results to a query and ranking possible results. This paper deals largely with the discovery and more specifically a process called web crawling.
	\end{abstract}
